Legion: Expressing Locality and Independence with Logical Regions

### 2012-04-27 doc/sc2012/circuit.tex
fix up dependenencies and references

Wires are simply partitioned in {\tt MAX\_PIECES} subregions (line 20).  
The nodes are first partitioned into 
{\em private} and {\em shared} nodes (line 21).  Private nodes
are touched by a single task in a phase, while shared nodes may
be referenced by multiple tasks in a phase.  The thick lines in figure \ref{sfig:part_fig:pvs}
show how the nodes in a small graph might be partitioned into three subsets.  Gray
nodes are shared and black nodes are private.  Note that
this partition is disjoint since each node has one color.
%Our current implementation uses small
%integers or booleans for the names of colors, but any enumerable set would be
%fine.  The coloring relation need not be total - it can leave out some elements entirely.  And although it is not required to be injective (it can map a single
%element to multiple colors), the fact that injective mappings will always
%result in disjoint subregions makes them strongly encouraged (when possible).
%Our example uses four colorings to create circuit partitions.

@@

Lines 36-40 form the bulk of the actual simulation, performing three passes
over the circuit in each iteration.  Each pass loops over an array of pieces (constructed on lines 30-34 from the partitions),
spawning a task for each piece.   There are no explicit requests for
parallel execution, nor is there synchronization required between the
passes.  Both the fact that the tasks can be run in parallel within a pass
and the required inter-pass dependencies are determined automatically
by the Legion runtime based on the region access annotations on the task declarations
(see Section~\ref{subsec:cirdependence}).

>>>>

Wires are simply partitioned in {\tt MAX\_PIECES} subregions (line 20).  
The nodes are first partitioned into 
{\em private} and {\em shared} nodes (line 21).  Private nodes
are touched by a single task in a phase, while shared nodes may
be referenced by multiple tasks in a phase.  The thick lines in Figure~\ref{sfig:part_fig:pvs}
show how the nodes in a small graph might be partitioned into three subsets.  Gray
nodes are shared and black nodes are private.  Note that
this partition is disjoint since each node has one color.
%Our current implementation uses small
%integers or booleans for the names of colors, but any enumerable set would be
%fine.  The coloring relation need not be total - it can leave out some elements entirely.  And although it is not required to be injective (it can map a single
%element to multiple colors), the fact that injective mappings will always
%result in disjoint subregions makes them strongly encouraged (when possible).
%Our example uses four colorings to create circuit partitions.

@@

Lines 36-40 form the bulk of the actual simulation, performing three passes
over the circuit in each iteration.  Each pass loops over an array of pieces (constructed on lines 30-34 from the partitions),
spawning a task for each piece.   There are no explicit requests for
parallel execution, nor is there synchronization required between the
passes.  Both the fact that the tasks can be run in parallel within a pass
and the required inter-pass dependencies are determined automatically
by the Legion runtime based on the region access annotations on the task declarations
(see Section~\ref{sec:soop}).

### 2012-04-27 doc/sc2012/code_ex.tex
fix up dependenencies and references

\lstset{
  captionpos=b,
  language=C++,
  basicstyle=\scriptsize,
  numbers=left,
  numberstyle=\tiny,
  columns=fullflexible,
  stepnumber=1,
  escapechar=\#,
  keepspaces=true,
  literate={<}{{$\langle$}}1 {>}{{$\rangle$}}1,
  morekeywords={region,coloring,partition,spawn,disjoint,aliased},
  deletekeywords=float,
}
\begin{lstlisting}[float={t},label={lst:code_ex},caption={Circuit Simulation Code Example}]
struct Node { float voltage, new_charge, capacitance; };
struct Wire<rn> { Node@rn in_node, out_node; float current, ... ; };
struct Circuit { region   r_all_nodes; /* contains all nodes for the circuit */
                 region   r_all_wires; /* contains all circuit wires */ };
struct CircuitPiece {
  region  rn_pvt, rn_shr, rn_ghost; /* private, shared, ghost node regions */
  region  rw_pvt;                   /* private wires region */ };

>>>>

\lstset{
  captionpos=b,
  language=C++,
  basicstyle=\scriptsize,
  numbers=left,
  numberstyle=\tiny,
  columns=fullflexible,
  stepnumber=1,
  escapechar=\#,
  keepspaces=true,
  literate={<}{{$\langle$}}1 {>}{{$\rangle$}}1,
  morekeywords={region,coloring,partition,spawn,disjoint,aliased},
  deletekeywords=float,
}
\begin{lstlisting}[float={t},label={lst:code_ex},caption={Circuit simulation.}]
struct Node { float voltage, new_charge, capacitance; };
struct Wire<rn> { Node@rn in_node, out_node; float current, ... ; };
struct Circuit { region   r_all_nodes; /* contains all nodes for the circuit */
                 region   r_all_wires; /* contains all circuit wires */ };
struct CircuitPiece {
  region  rn_pvt, rn_shr, rn_ghost; /* private, shared, ghost node regions */
  region  rw_pvt;                   /* private wires region */ };

### 2012-04-27 doc/sc2012/legion.tex
fix up dependenencies and references

\item We present the results of experiments on four applications: fluid-flow on a regular grid,
a three-level AMR code solving a simple heat transfer equation, a circuit simulation,
and LINPACK.  We run each of these four codes and best available reference versions on three different
clusters of multicore processors with attached GPUs: a small cluster of our own, a medium-sized cluster designed for visualization applications, and up to half of the Keeneland supercomputer (Section~\ref{sec:results}).

\end{itemize}
%\input{circuit}
\input{code_ex}
%\input{part_fig}

%\input{type_system}
%\input{exec}

%\input{highlevel}
%\input{mapping_fig}

%\input{lowlevel}
%\input{experiments}
%\input{related}
%\input{conclusion}

\bibstyle{IEEEtran}
{
\tiny
\bibliography{bibliography}
}

>>>>

\item We present the results of experiments on four applications: fluid-flow on a regular grid,
a three-level AMR code solving a simple heat transfer equation, a circuit simulation,
and LINPACK.  We run each of these four codes and best available reference versions on three different
clusters of multicore processors with attached GPUs: a small cluster of our own, a medium-sized cluster designed for visualization applications, and up to half of the Keeneland supercomputer (Section~\ref{sec:exp}).

\end{itemize}
\input{code_ex}
\input{circuit}
\input{part_fig}
\input{soop}
\input{mapping}cir
\input{experiments}
\input{related}
\input{conclusion}

%\input{mapping_fig}

\bibstyle{IEEEtran}
\bibliography{bibliography}
